Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-06-15 BD_radvel/kurosawa.tex
Fixed minor typo found by Stu.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@743 25464f21-6099-402c-b30a-640f1d40d38b

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of the $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. This reassures that our uncertainties in RV values are
reasonable, and an additional systematic error may not be necessary in
this analysis. 
The boundary ($p=10^{-3}$) between the RV variable and the RV
constants seems somewhat arbitrary, but here we simply adopt the
definition of \citet{maxted:2005}.  Based on this criteria, there are
four objects which show significant RV variations (out of 17 samples)
as one can see from the figure.   They are USco~112, USco~128,
USco~40, and USco~55, and considered as our preliminary binary/multiple 
candidates.  We will discuss the binary fraction and the expected binary
detection probability later in Section~\ref{sec:Binary-fraction}.

@@

% The observed binary fraction is expected to be sensitive to the
% assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
% the RV shifts and the systematic errors are in the same order of
% magnitude. The number of binary detections would decrease as
% $\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
% probabilities ($p$) for each object being a RV constant object as done
% earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
% systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
% the uncertainties in the RVs of each object.  The results are
% summarised in Table~\ref{tab:prob_compare} along with the probabilities
% computed without the systematic error (as in
% Section\ref{sub:Radial-velocities}).  The number of objects with
% $p<10^{-3}$ decreases from 4 to 2 as the systematic error is
% introduced. Unfortunately, the probabilities computed with
% $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
% below the $p=10^{-3}$ boundary value; hence, they become RV constant
% objects as the systematic error is introduced. This
% clearly demonstrates the importance of the uncertainty estimates in
% the measured RV values.  We found that the histogram of the $\chi^2$
% probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
% Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
% expected distribution of $-\log{p}$ (not shown here).  
% The binary fraction estimated with the assumed systematic error is
% $2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
%
% %
% This may be out of place =======================
An alternative explanation for the RV variations found in the binary
candidates above is a type of stellar pulsations found by
\citet{palla:2005}. They studied the non-adiabatic, linear
instability of very VLM stars and BD during the deturium burning phase
in the core, and found unstable fundamental modes in the time-scale
between $\sim 1$ and $\sim 5$~h for the object mass from $0.02$ and
$0.1\,\Msun$.  By using their pulsation periods and by assuming that the
pulsation amplitudes is 5~per~cent of the radius of the objects, we
find that the expected RV variation can be $>6\,\kmps$.
As mentioned in Section~\ref{sec:observation-reduction}, for each object at a
given night, two separate spectra are obtained consecutively (with
time separations of $\sim 0.5$~h.). Before co-adding the two spectra
together, we have measured the RV from each spectrum to check if there
is a large jump in the RV measurements in short
time-scale. The size of the shifts in the RV values measured in the two
consecutive spectra are found in between $0.02\pm0.10$ (USco~128)
and  $2.04\pm1.67\,\kmps$ (USco~66), and the average size of the
shifts $0.36\,\kmps$, which is much smaller than the
expected RV variation based on the models of \citet{palla:2005};
hence, found little indication of the pulsations in our sample.

@@

We thank the staff of VLT of the ESO for carrying out the observations
in service mode. RK is grateful for Rob Jeffries  and Tim Naylor for helpful
suggestions on the data analysis presented in this paper. We also
thank Matteww Bate for providing us valuable comments on
the manuscript. This work was supported by PPARC rolling grant
PP/C501609/1.

>>>>

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. This reassures that our uncertainties in RV values are
reasonable, and an additional systematic error may not be necessary in
this analysis. 
The boundary ($p=10^{-3}$) between the RV variable and the RV
constants seems somewhat arbitrary, but here we simply adopt the
definition of \citet{maxted:2005}.  Based on this criteria, there are
four objects which show significant RV variations (out of 17 samples)
as one can see from the figure.   They are USco~112, USco~128,
USco~40, and USco~55, and considered as our preliminary binary/multiple 
candidates.  We will discuss the binary fraction and the expected binary
detection probability later in Section~\ref{sec:Binary-fraction}.

@@

% The observed binary fraction is expected to be sensitive to the
% assumed size of the systematic error ($\sigma_{\mathrm{sys}}$) since
% the RV shifts and the systematic errors are in the same order of
% magnitude. The number of binary detections would decrease as
% $\sigma_{\mathrm{sys}}$ increases.  We have computed the $\chi^2$
% probabilities ($p$) for each object being a RV constant object as done
% earlier (Section\ref{sub:Radial-velocities}), but with the assumed 
% systematics error of $\sigma_{\mathrm{sys}}=0.2\,\kmps$, which was added to
% the uncertainties in the RVs of each object.  The results are
% summarised in Table~\ref{tab:prob_compare} along with the probabilities
% computed without the systematic error (as in
% Section\ref{sub:Radial-velocities}).  The number of objects with
% $p<10^{-3}$ decreases from 4 to 2 as the systematic error is
% introduced. Unfortunately, the probabilities computed with
% $\sigma_{\mathrm{sys}}=0.0\,\kmps$ for GY~141 and USco~55 are just
% below the $p=10^{-3}$ boundary value; hence, they become RV constant
% objects as the systematic error is introduced. This
% clearly demonstrates the importance of the uncertainty estimates in
% the measured RV values.  We found that the histogram of the $\chi^2$
% probabilities with $\sigma_{\mathrm{sys}}=0.2\,\kmps$ (as in
% Fig~\ref{fig:chisq-test}), is also in reasonable agreement with the
% expected distribution of $-\log{p}$ (not shown here).  
% The binary fraction estimated with the assumed systematic error is
% $2/17$ or $f=12^{+13}_{-8}$~per~cent for $a<0.1$~au.
%
% %
% This may be out of place =======================
An alternative explanation for the RV variations found in the binary
candidates above is a type of stellar pulsations found by
\citet{palla:2005}. They studied the non-adiabatic, linear
instability of very VLM stars and BD during the deturium burning phase
in the core, and found unstable fundamental modes in the time-scale
between $\sim 1$ and $\sim 5$~h for the object mass from $0.02$ and
$0.1\,\Msun$.  By using their pulsation periods and by assuming that the
pulsation amplitudes is 5~per~cent of the radius of the objects, we
find that the expected RV variation can be $>6\,\kmps$.
As mentioned in Section~\ref{sec:observation-reduction}, for each object at a
given night, two separate spectra are obtained consecutively (with
time separations of $\sim 0.5$~h.). Before co-adding the two spectra
together, we have measured the RV from each spectrum to check if there
is a large jump in the RV measurements in short
time-scale. The size of the shifts in the RV values measured in the two
consecutive spectra are found in between $0.02\pm0.10$ (USco~128)
and  $2.04\pm1.67\,\kmps$ (USco~66), and the average size of the
shifts $0.36\,\kmps$, which is much smaller than the
expected RV variation based on the models of \citet{palla:2005};
hence, we found little indication of the pulsations in our sample.

@@

We thank the staff of VLT of the ESO for carrying out the observations
in service mode. RK is grateful for Rob Jeffries  and Tim Naylor for helpful
suggestions on the data analysis presented in this paper. We also
thank Matthew Bate for providing us valuable comments on
the manuscript. This work was supported by PPARC rolling grant
PP/C501609/1.
